```{r}
library(rio)
library(dplyr)
library(usethis)
path_i <- "~/Documents/Estadistica/estadisticaFcaUnl/data/internal"
```



## Pesada terneros
#done
```{r}
pesada_terneros <- import(file.path(path_i, "pesada_terneros.xlsx"))
str(pesada_terneros)
```
```{r}
use_data(pesada_terneros, overwrite = TRUE)
```

## superficies_EAP
#done
```{r}
superficies_EAP <- read.fwf(file.path(path_i, "superficies_EAP.txt"), widths = c(23, 10, 20), header = FALSE, skip = 1, strip.white = TRUE, col.names = c("Departamento", "Cant_EAP", "Sup_promedio")) %>%
    mutate(Departamento = gsub('"', "", Departamento))
str(superficies_EAP)
```
```{r}
use_data(superficies_EAP, overwrite = TRUE)
```

## pesada_novillos
#done
```{r}
pesada_novillos <- import(file.path(path_i, "pesada_novillos.xlsx")) %>%
    mutate(
        Fecha_Ingreso = as.Date(as.numeric(Fecha_Ingreso), origin = "1899-12-30"),
        Fecha = as.Date(as.numeric(Fecha), origin = "1899-12-30"),
        Hora = format(as.POSIXct(as.numeric(Hora) * 86400, origin = "1970-01-01", tz = "UTC"), "%H:%M:%S")
    ) %>%
    rename(
        Dias = Días,
        Dias_total = Días_total
    )
str(pesada_novillos)
```
```{r}
use_data(pesada_novillos, overwrite = TRUE)
```

## tambos_2008_2015
#done
```{r}
tambos_2008_2015 <- import(file.path(path_i, "tambos_2008-2015.xls"))
str(tambos_2008_2015)
```
```{r}
use_data(tambos_2008_2015, overwrite = TRUE)
```

## lotes_BA
#done
```{r}
lotes_BA <- import(file.path(path_i, "Lotes_BA.xls"))
str(lotes_BA)
```
```{r}
use_data(lotes_BA, overwrite = TRUE)
```

## riesgo_arbolado
#done
```{r}
riesgo_arbolado <- import(file.path(path_i, "riesgo_arbolado.xlsx"))
str(riesgo_arbolado)
```
```{r}
use_data(riesgo_arbolado, overwrite = TRUE)
```

## ryegrass
#done
```{r}
ryegrass <- import(file.path(path_i, "ryegrass.txt"))
str(ryegrass)
```
```{r}
ryegrass <- ryegrass %>%
    mutate(
        planta = as.numeric(planta),
        longitud = as.numeric(longitud)
    )
str(ryegrass)
```
```{r}
use_data(ryegrass, overwrite = TRUE)
```

## tribolium
#done
```{r}
tribolium <- import(file.path(path_i, "tribolium.txt"))
str(tribolium)
```
```{r}
use_data(tribolium, overwrite = TRUE)
```

## lisina_pollos
#done
```{r}
lisina_pollos <- import(file.path(path_i, "lisina_pollos.txt"))
str(lisina_pollos)
```
```{r}
lisina_pollos <- lisina_pollos %>%
    mutate(
        Pollo = as.numeric(Pollo),
        Consumo = as.numeric(Consumo),
        Lisina = as.numeric(Lisina)
    )
str(lisina_pollos)
```
```{r}
use_data(lisina_pollos, overwrite = TRUE)
```

## productores
#done
```{r}
productores <- import(file.path(path_i, "productores.xlsx"))
str(productores)
```
```{r}
use_data(productores, overwrite = TRUE)
```

## especies
#done
```{r}
especies <- import(file.path(path_i, "especies.xlsx")) %>%
    rename(Numero = Número)
str(especies)
```
```{r}
use_data(especies, overwrite = TRUE)
```

## plantacion
#done
```{r}
set.seed(1)
altura <- round(rnorm(10, 2.5, sqrt(0.35)), 2)
cat(altura)
plantacion <- as.data.frame(altura)
str(plantacion)
```

```{r}
use_data(plantacion, overwrite = TRUE)
```

## plantacion_dap
#done
```{r}
set.seed(1)
dap <- round(rnorm(10, 15, sqrt(1.5)), 2)
cat(dap)
plantacion_dap <- as.data.frame(dap)
str(plantacion_dap)
```

```{r}
use_data(plantacion_dap, overwrite = TRUE)
```

## pulsaciones_caballos
#done
```{r}
set.seed(3)
pulsaciones <- round(rnorm(15, mean = 85, sd = 15))
cat(pulsaciones)
pulsaciones_caballos <- as.data.frame(pulsaciones)
str(pulsaciones_caballos)
```

```{r}
use_data(pulsaciones_caballos, overwrite = TRUE)
```

## molinos
#done
```{r}
set.seed(4)
km_h <- round(rnorm(15, 78, 3), 0)
cat(km_h)
molinos <- as.data.frame(km_h)
str(molinos)
```
```{r}
use_data(molinos, overwrite = TRUE)
```

## alimento
#done
```{r}
set.seed(8)
vitaminas <- round(rnorm(16, 13, 2.5), 1)
cat(vitaminas)
alimento <- as.data.frame(vitaminas)
str(alimento)
```
```{r}
use_data(alimento, overwrite = TRUE)
```

## maiz
#done
```{r}
maiz <- data.frame(plantas = 6:11, parcelas = c(2, 5, 6, 4, 2, 1))
str(maiz)
```
```{r}
use_data(maiz, overwrite = TRUE)
```

## corderos
#done
```{r}
set.seed(16)
peso <- round(rnorm(20, 45, 1.8), 2)
cat(peso, sep = ", ")
corderos <- as.data.frame(peso)
str(corderos)
```

```{r}
use_data(corderos, overwrite = TRUE)
```

## sorgo
#done
```{r}
set.seed(1)
altura <- round(rnorm(16, 2, 0.1), 2)
cat(altura, sep = ", ")
sorgo <- as.data.frame(altura)
str(sorgo)
```
```{r}
use_data(sorgo, overwrite = TRUE)
```

## ovejas
#done
```{r}
set.seed(3)
peso <- round(rnorm(25, 10, 2), 1)
cat(peso, sep = ", ")
ovejas <- as.data.frame(peso)
str(ovejas)
```
```{r}
use_data(ovejas, overwrite = TRUE)
```

## balanceado_cerdos
#done
```{r}
set.seed(4)
aumento <- round(rnorm(20, 187, 27))
cat(aumento, sep = ", ")
balanceado_cerdos <- as.data.frame(aumento)
str(balanceado_cerdos)
```
```{r}
use_data(balanceado_cerdos, overwrite = TRUE)
```

## pezoneras
#done
```{r}
duracion <- c(970, 1530, 1120, 1240, 1310, 1515, 1302, 1221, 985, 1312, 1721, 1200, 1305, 1000, 1040, 1450, 1342, 1221, 1310, 1500)
cat(duracion, sep = " ")
pezoneras <- as.data.frame(duracion)
str(pezoneras)
```
```{r}
use_data(pezoneras, overwrite = TRUE)
```

## establecimientos
#done
```{r}
set.seed(6)
superficie <- round(rnorm(12, 130, 30))
cat(superficie, sep = ", ")
establecimientos <- as.data.frame(superficie)
str(establecimientos)
```
```{r}
use_data(establecimientos, overwrite = TRUE)
```

## neumaticos_tractores
#done
```{r}
set.seed(19)
duracion <- round(rnorm(15, 27.63, sqrt(11.5)), 2)
cat(duracion, sep = ", ")
neumaticos_tractores <- as.data.frame(duracion)
str(neumaticos_tractores)
```
```{r}
use_data(neumaticos_tractores, overwrite = TRUE)
```

## glifosato
#done
```{r}
glifosato <- import(file.path(path_i, "glifosato.xlsx"))
str(glifosato)
```
```{r}
use_data(glifosato, overwrite = TRUE)
```

## barrenador
#done
```{r}
barrenador <- import(file.path(path_i, "barrenador.xlsx"))
str(barrenador)
```
```{r}
use_data(barrenador, overwrite = TRUE)
```

## penetrometro
#done
```{r}
penetrometro <- import(file.path(path_i, "penetrometro.xlsx"))
str(penetrometro)
```
```{r}
use_data(penetrometro, overwrite = TRUE)
```

## TRC
#done
```{r}
TRC <- import(file.path(path_i, "TRC.xlsx"))
str(TRC)
```
```{r}
use_data(TRC, overwrite = TRUE)
```

## concentracion_insecticida
```{r}
metA <- c(10.7, 11.2, 15.3, 14.9, 13.9, 15, 15.6, 15.7, 14.3, 10.8)
metB <- c(11.1, 11.4, 15, 15.1, 14.3, 15.4, 15.4, 16, 14.3, 11.2)
n1 <- length(metA)
n2 <- length(metB)


concentracion_insecticida <- data.frame(
    metodo = c(rep("A", n1), rep("B", n2)),
    concentracion = c(metA, metB)
) %>%
    mutate(metodo = factor(metodo, levels = c("A", "B")))
str(concentracion_insecticida)
```
```{r}
use_data(concentracion_insecticida, overwrite = TRUE)
```

## neumaticos
#done
```{r}
set.seed(1)
A <- round(rnorm(15, 25.75, 0.45), 1)
B <- round(rnorm(15, 23.20, 0.45), 1)

neumaticos <- data.frame(
    neumatico = c(1:(length(A) + length(B))),
    marca = c(rep("A", length(A)), rep("B", length(B))),
    duracion = c(A, B)
)
str(neumaticos)
```
```{r}
use_data(neumaticos, overwrite = TRUE)
```

## peso_balanceado
#done
```{r}
set.seed(3)
muestra1 <- round(rnorm(25, 18.5, 3.8), 1)
muestra2 <- round(rnorm(30, 20.5, 3.8), 1)

muestra <- c(1:(length(muestra1) + length(muestra2)))
peso_balanceado <- data.frame(muestra,
    dia = c(
        rep("muestra1", length(muestra1)),
        rep("muestra2", length(muestra2))
    ),
    peso = c(muestra1, muestra2)
)
str(peso_balanceado)
```
```{r}
use_data(peso_balanceado, overwrite = TRUE)
```

## raciones
#done
```{r}
set.seed(4)
racion1 <- round(rnorm(12, 6.900, sqrt(0.65)), 1)
racion2 <- round(rnorm(12, 5.915, sqrt(0.65)), 1)
novillo <- c(1:(length(racion1) + length(racion2)))
raciones <- data.frame(novillo,
    racion = c(
        rep("1", length(racion1)),
        rep("2", length(racion2))
    ),
    peso = c(racion1, racion2)
)
str(raciones)
```
```{r}
use_data(raciones, overwrite = TRUE)
```

## cerdos
#done
```{r}
alim_d <- c(8.5, 8.2, 7.0, 8.3, 7.2, 8.1, 7.5, 7.8)
alim_m <- c(8.3, 8.5, 8.0, 8.4, 8.3, 8.1, 8.2, 8.1)
cerdo <- c(1:(length(alim_d) + length(alim_d)))
cerdos <- data.frame(cerdo,
    alimento = c(
        rep("alim_d", length(alim_d)),
        rep("alim_m", length(alim_m))
    ),
    ganancia = c(alim_d, alim_m)
)
str(cerdos)
```
```{r}
use_data(cerdos, overwrite = TRUE)
```

## ganancia_novillos
#done
```{r}
Placebo <- c(79, 60, 99, 68, 91, 99, 106, 68, 85, 56, 112, 93, 81, 96)
Mineral <- c(64, 142, 153, 119, 137, 88, 115, 90, 107, 98, 96, 80, 113, 97)
novillo <- c(1:(length(Placebo) + length(Mineral)))
ganancia_novillos <- data.frame(novillo,
    tratamiento = c(
        rep("Placebo", length(Placebo)),
        rep("Mineral", length(Mineral))
    ),
    ganancia = c(Placebo, Mineral)
)
str(ganancia_novillos)
```
```{r}
use_data(ganancia_novillos, overwrite = TRUE)
```

## N_suelo
#done
```{r}
set.seed(1)
Bueno <- round(rnorm(25, 21.5, 0.75), 1)
Pobre <- round(rnorm(25, 7.3, 0.45), 1)

N_suelo <- data.frame(
    suelo = c(1:(length(Bueno) + length(Pobre))),
    tipo = c(rep("Bueno", length(Bueno)), rep("Pobre", length(Pobre))),
    ppm = c(Bueno, Pobre)
)
str(N_suelo)
```
```{r}
use_data(N_suelo, overwrite = TRUE)
```

## efectividad_sembradora
#done
```{r}
nueva <- c(8.0, 8.4, 8.0, 6.4, 8.6, 7.7, 7.7, 5.6, 5.7, 6.2)
vieja <- c(5.6, 7.4, 7.3, 6.4, 7.5, 6.1, 6.6, 6.0, 5.6, 5.5)
parcelas <- c(1:(length(nueva) + length(vieja)))
efectividad_sembradora <- data.frame(parcelas,
    maquina = c(
        rep("nueva", length(nueva)),
        rep("vieja", length(vieja))
    ),
    rendimiento = c(nueva, vieja)
)
str(efectividad_sembradora)
```
```{r}
use_data(efectividad_sembradora, overwrite = TRUE)
```

## lesiones_hojas
#done
```{r}
prep1 <- c(9, 17, 31, 18, 7, 8, 20, 10)
prep2 <- c(17, 11, 18, 14, 6, 7, 17, 5)
id <- c(1:(length(prep1) + length(prep2)))
lesiones_hojas <- data.frame(id,
    preparado = c(
        rep("prep1", length(prep1)),
        rep("prep2", length(prep2))
    ),
    lesiones = c(prep1, prep2)
)
str(lesiones_hojas)
```
```{r}
use_data(lesiones_hojas, overwrite = TRUE)
```

## dieta_bufalos
#done
```{r}
inicial <- c(70, 75, 77, 80, 85, 90, 74, 92, 89, 88)
final <- c(65, 68, 70, 76, 83, 82, 70, 88, 83, 82)
animal <- c(1:(length(inicial) + length(final)))
dieta_bufalos <- data.frame(animal,
    tratamiento = c(
        rep("inicial", length(inicial)),
        rep("final", length(final))
    ),
    perdida = c(inicial, final)
)
str(dieta_bufalos)
```
```{r}
use_data(dieta_bufalos, overwrite = TRUE)
```

## colesterol
#done
```{r}
set.seed(13)
baja_grasa <- round(rnorm(19, 167.16, sqrt(198)), 1)
normal <- round(rnorm(24, 178.12, sqrt(435)), 1)
paciente <- c(1:(length(baja_grasa) + length(normal)))
colesterol <- data.frame(paciente,
    tratamiento = c(
        rep("baja_grasa", length(baja_grasa)),
        rep("normal", length(normal))
    ),
    colesterol = c(baja_grasa, normal)
)
str(colesterol)
```
```{r}
use_data(colesterol, overwrite = TRUE)
```

## MS_girasol
#done
```{r}
Normales <- c(6.21, 5.70, 6.04, 4.47, 5.22, 4.45, 4.84, 5.88, 5.82, 6.09, 5.59, 6.06, 5.59, 6.74, 5.55, 5.79)
Anormales <- c(4.28, 3.71, 2.48, 3.71, 3.37, 4.20, 5.06, 2.40, 4.93, 4.91, 3.51, 4.36, 3.80, 2.99)
plantas <- c(1:(length(Normales) + length(Anormales)))
MS_girasol <- data.frame(plantas,
    grupo = c(
        rep("Normales", length(Normales)),
        rep("Anormales", length(Anormales))
    ),
    MS = c(Normales, Anormales)
)
str(MS_girasol)
```
```{r}
use_data(MS_girasol, overwrite = TRUE)
```

## dietas_pollos
#done
```{r}
Tradicional <- c(1.75, 1.43, 1.72, 1.58, 1.62, 1.72, 1.75, 1.80)
Especial <- c(1.80, 1.52, 1.80, 1.59, 1.71, 1.78, 1.75, 1.81)
pollo <- c(1:(length(Tradicional) + length(Especial)))
dietas_pollos <- data.frame(pollo,
    dieta = c(
        rep("Tradicional", length(Tradicional)),
        rep("Especial", length(Especial))
    ),
    ganancia = c(Tradicional, Especial)
)
str(dietas_pollos)
```
```{r}
use_data(dietas_pollos, overwrite = TRUE)
```

## germinacion
```{r}
txt <- textConnection(
    "Trat   Germinado  semillas
  A       si         190
  A       no         10
  B       si         170
  B       no         30
  C       si         180
  C       no         20"
)
germinacion <- read.table(txt, header = T)
xtabs(semillas ~ Trat + Germinado, germinacion)
str(germinacion)
```
```{r}
use_data(germinacion, overwrite = TRUE)
```

## algodon
```{r}
txt <- textConnection(
    "corola  hoja    frec
  amarilla ancha   717
  amarilla angosta 249
  blanca   ancha   236
  blanca   angosta 80"
)
algodon <- read.table(txt, header = T)
xtabs(frec ~ corola + hoja, algodon)
str(algodon)
```
```{r}
use_data(algodon, overwrite = TRUE)
```

## educacion
```{r}
tbl <- matrix(c(775, 687, 76, 170),
    byrow = T, nrow = 2,
    dimnames = list(casado = c("si", "no"), momento = c("ingreso", "al 3er año"))
)
txt <- textConnection(
    "momento       casado    frec
  ingreso        si        775
  ingreso        no        76
  3er_año        si        687
  3er_año        no        170"
)
educacion <- read.table(txt, header = T)
xtabs(frec ~ momento + casado, educacion)
str(educacion)
```
```{r}
use_data(educacion, overwrite = TRUE)
```

## semilla
```{r}
tbl <- matrix(
    c(
        45, 27, 24, 19, 32, 26, 88, 22, 28, 25,
        12, 8, 7, 10, 11, 6, 24, 10, 6, 7
    ),
    byrow = F, nrow = 10,
    dimnames = list(plantas = 1:10, "tipo semilla" = c("redonda", "angular"))
)
tbl

semilla <- data.frame(
    redonda = c(45, 27, 24, 19, 32, 26, 88, 22, 28, 25),
    angular = c(12, 8, 7, 10, 11, 6, 24, 10, 6, 7)
)
str(semilla)
```
```{r}
use_data(semilla, overwrite = TRUE)
```

## albumen
```{r}
tbl <- matrix(
    c(
        25, 32, 14, 70, 24, 20, 32, 44, 50, 44,
        11, 7, 5, 27, 13, 6, 13, 9, 14, 18
    ),
    byrow = F, ncol = 2,
    dimnames = list(plantas = 1:10, "albumen" = c("amarillo", "verde"))
)
tbl
albumen <- data.frame(
    amarillo = c(25, 32, 14, 70, 24, 20, 32, 44, 50, 44),
    verde = c(11, 7, 5, 27, 13, 6, 13, 9, 14, 18)
)
str(albumen)
```
```{r}
use_data(albumen, overwrite = TRUE)
```

## insectos
```{r}
tbl <- matrix(c(213, 128, 37, 18, 3, 1),
    byrow = F, ncol = 1,
    dimnames = list(insectos = 0:5, "frecuencia")
)
tbl
# datos
insectos <- c(0:5)
obs <- c(213, 128, 37, 18, 3, 1)
insectos <- data.frame(obs, insectos)
str(insectos)
```
```{r}
use_data(insectos, overwrite = TRUE)
```

## monedas
```{r}
tbl <- matrix(c(6, 41, 56, 45, 12),
    byrow = F, ncol = 1,
    dimnames = list(caras = 0:4, "frecuencia")
)
tbl
caras <- 0:4
obs <- c(6, 41, 56, 45, 12)
monedas <- data.frame(obs, caras)
str(monedas)
```
```{r}
use_data(monedas, overwrite = TRUE)
```

## capturados
```{r}
tbl <- matrix(c(381, 360, 173, 65, 13, 8),
    byrow = F, ncol = 1,
    dimnames = list(insectos = 0:5, "intervalos")
)
tbl
obs <- c(381, 360, 173, 65, 13, 8)
insectos <- c(0, 1, 2, 3, 4, 5)
capturados <- data.frame(obs, insectos)
str(capturados)
```
```{r}
use_data(capturados, overwrite = TRUE)
```

## susceptibilidad
```{r}
tbl <- matrix(c(15, 30, 40, 2, 3, 10),
    byrow = T, ncol = 3,
    dimnames = list(Roya = c("resistente", "susceptible"), "largo semilla" = c("corto", "medio", "largo"))
)
txt <- textConnection(
    "Roya               largo           freq
  resistente            corto          15
  resistente            medio          2
  resistente            largo          30
  susceptible            corto         3
  susceptible            medio         40
  susceptible            largo         10"
)
susceptibilidad <- read.table(txt, header = T)
xtabs(freq ~ Roya + largo, susceptibilidad)
str(susceptibilidad)
```
```{r}
use_data(susceptibilidad, overwrite = TRUE)
```

## actividad
```{r}
txt <- textConnection("actividad	localidad	freq
Agrícola	A	40
Agrícola	B	32
Agrícola	C	59
Agrícola	D	65
Ganadera	A	51
Ganadera	B	87
Ganadera	C	42
Ganadera	D	53
Mixta	A	120
Mixta	B	68
Mixta	C	55
Mixta	D	92
")
actividad <- read.table(txt, header = T)
xtabs(freq ~ localidad + actividad, actividad)
str(actividad)
```
```{r}
use_data(actividad, overwrite = TRUE)
```

## razas
```{r}
razas <- read.table(textConnection(
    "Tipo    Raza     partos
    anormal   Holstein 42
    anormal   Cruza    20
    anormal   Jersey   30
    normal  Holstein 130
    normal  Cruza    28
    normal  Jersey   50"
), header = T)
xtabs(partos ~ Tipo + Raza, razas)
str(razas)
```
```{r}
use_data(razas, overwrite = TRUE)
```

## semillas
```{r}
semillas <- read.table(textConnection(
    "Partida    Tamaño    semillas
    A           grande    70
    A           normal    290
    A           chico     90
    B           grande    80
    B           normal    300
    B           chico     110
    C           grande    20
    C           normal    140
    C           chico     60"
), header = T)
xtabs(semillas ~ Partida + Tamaño, semillas)
str(semillas)
```
```{r}
use_data(semillas, overwrite = TRUE)
```

## arvejas
```{r}
arvejas <- data.frame(
    freq = c(315, 108, 101, 32),
    fenotipo = c("LA", "LV", "RA", "RV")
)
str(arvejas)
```
```{r}
use_data(arvejas, overwrite = TRUE)
```

## agua_forrajera
```{r}
agua_forrajera <- data.frame(agua = c(12, 18, 24, 30, 36), MS = c(5.27, 5.68, 6.25, 7.53, 8.02))
str(agua_forrajera)
```
```{r}
use_data(agua_forrajera, overwrite = TRUE)
```

## area_trigo
```{r}
area_trigo <- data.frame(
    sup_total = c(147, 125, 160, 118, 149, 128, 150, 145, 115, 140, 152, 152),
    sup_trigo = c(56, 42, 72, 36, 63, 47, 55, 49, 38, 42, 68, 60)
)
str(area_trigo)
```
```{r}
use_data(area_trigo, overwrite = TRUE)
```

## coleoptero
```{r}
coleoptero <- data.frame(
    HR = c(0, 12, 29.5, 43, 53, 62.5, 75.5, 85, 93),
    perdida = c(8.98, 8.14, 6.67, 6.08, 5.90, 5.83, 4.68, 4.20, 3.72)
)
str(coleoptero)
```
```{r}
use_data(coleoptero, overwrite = TRUE)
```

## P_maiz
```{r}
P_maiz <- data.frame(
    P_suelo = c(0.4, 3.1, 4.7, 9.4, 11.6, 10.9, 23.1, 23.1, 29.9),
    P_planta = c(64, 71, 54, 81, 98, 76, 76, 95, 99)
)
str(P_maiz)
```
```{r}
use_data(P_maiz, overwrite = TRUE)
```

## lluvia_forraje
```{r}
lluvia_forraje <- data.frame(
    rend = c(2, 1, 5, 3, 6, 4, 8, 9, 10, 7),
    lluvia = c(3, 6, 9, 12, 15, 18, 21, 24, 27, 30)
)
str(lluvia_forraje)
```
```{r}
use_data(lluvia_forraje, overwrite = TRUE)
```

## hileras_maiz
```{r}
hileras_maiz <- import(file.path(path_i, "hileras_maiz.xlsx"))
str(hileras_maiz)
```
```{r}
use_data(hileras_maiz, overwrite = TRUE)
```

## calificaciones
```{r}
calificaciones <- data.frame(
    Fisica = c(65, 73, 87, 64, 78, 92, 70, 66, 88, 87, 79, 71),
    Matematica = c(68, 76, 88, 65, 79, 96, 78, 65, 81, 87, 78, 70)
)
str(calificaciones)
```
```{r}
use_data(calificaciones, overwrite = TRUE)
```

## semilla_trigo
```{r}
semilla_trigo <- import(file.path(path_i, "semilla_trigo.xlsx"))
str(semilla_trigo)
```
```{r}
use_data(semilla_trigo, overwrite = TRUE)
```

## huevos
```{r}
huevos <- import(file.path(path_i, "huevos.xlsx"))
str(huevos)
```
```{r}
use_data(huevos, overwrite = TRUE)
```

## pollos
```{r}
pollos <- import(file.path(path_i, "pollos.xlsx"))
str(pollos)
```
```{r}
use_data(pollos, overwrite = TRUE)
```

## fungicida
```{r}
fungicida <- import(file.path(path_i, "fungicida.xlsx"))
str(fungicida)
```
```{r}
use_data(fungicida, overwrite = TRUE)
```

## proteina_caseina
```{r}
proteina_caseina <- import(file.path(path_i, "proteina_caseina.xlsx"))
str(proteina_caseina)
```
```{r}
use_data(proteina_caseina, overwrite = TRUE)
```

## dosis_tomate
```{r}
dosis_tomate <- import(file.path(path_i, "dosis_tomate.xlsx"))
str(dosis_tomate)
```
```{r}
use_data(dosis_tomate, overwrite = TRUE)
```