---
title: "Importación y guardado de datasets"
output: html_document
---

```{r setup, include=FALSE}
library(rio)
library(dplyr)
library(usethis)

path_i <- "~/Documents/Estadistica/estadisticaFcaUnl/data/internal"
```

## 1. vitA_vaquillas
```{r}
name <- "vitA_vaquillas"
vitA_vaquillas <- import(paste0(path_i, "/", name, ".xlsx"))
str(vitA_vaquillas)
```
```{r}
vitA_vaquillas <- vitA_vaquillas %>%
  mutate(
    Tratamiento = as.factor(Tratamiento)
  )
str(vitA_vaquillas)
```
```{r}
use_data(vitA_vaquillas)
```

## 2. dms_ensilaje
```{r}
name <- "dms_ensilaje"
dms_ensilaje <- import(paste0(path_i, "/", name, ".xlsx"))
str(dms_ensilaje)
```
```{r}
dms_ensilaje <- dms_ensilaje %>%
  mutate(
    Trat = as.factor(Trat)
  )
str(dms_ensilaje)
```
```{r}
use_data(dms_ensilaje)
```

## 3. guayule
```{r}
name <- "guayule"
guayule <- import(paste0(path_i, "/", name, ".xlsx"))
str(guayule)
```
```{r}
guayule <- guayule %>%
  mutate(
    Tipo = as.factor(Tipo)
  )
str(guayule)
```
```{r}
use_data(guayule)
```

## 4. ace_codornices
```{r}
name <- "ace_codornices"
ace_codornices <- import(paste0(path_i, "/", name, ".xlsx"))
str(ace_codornices)
```
```{r}
ace_codornices <- ace_codornices %>%
  mutate(
    Momento = as.factor(Momento)
  )
str(ace_codornices)
```
```{r}
use_data(ace_codornices)
```

## 5. nectar_trebol_rojo
```{r}
name <- "nectar_trebol_rojo"
nectar_trebol_rojo <- import(paste0(path_i, "/", name, ".xlsx"))
str(nectar_trebol_rojo)
```
```{r}
nectar_trebol_rojo <- nectar_trebol_rojo %>%
  mutate(
    Cabeza = as.factor(Cabeza),
    Presion = as.factor(Presion)
  )
str(nectar_trebol_rojo)
```
```{r}
use_data(nectar_trebol_rojo)
```

## 6. trebol_rizhobium
```{r}
name <- "trebol_rizhobium"
trebol_rizhobium <- import(paste0(path_i, "/", name, ".xlsx"))
str(trebol_rizhobium)
```
```{r}
trebol_rizhobium <- trebol_rizhobium %>%
  mutate(
    Tratamiento = as.factor(Tratamiento)
  )
str(trebol_rizhobium)
```
```{r}
use_data(trebol_rizhobium)
```

## 7. dieta_cerdos
```{r}
name <- "dieta_cerdos"
dieta_cerdos <- import(paste0(path_i, "/", name, ".xlsx"))
str(dieta_cerdos)
```
```{r}
dieta_cerdos <- dieta_cerdos %>%
  mutate(
    D = as.factor(D)
  )
str(dieta_cerdos)
```
```{r}
use_data(dieta_cerdos)
```

## 8. caballos
```{r}
name <- "caballos"
caballos <- import(paste0(path_i, "/", name, ".xlsx"))
str(caballos)
```
```{r}
caballos <- caballos %>%
  mutate(
    TR = as.factor(TR)
  )
str(caballos)
```
```{r}
use_data(caballos)
```

## 9. tomate
```{r}
name <- "tomate"
tomate <- import(paste0(path_i, "/", name, ".xlsx"))
str(tomate)
```
```{r}
tomate <- tomate %>%
  mutate(
    Tejido = as.factor(Tejido),
    TR = as.factor(TR)
  )
str(tomate)
```
```{r}
use_data(tomate)
```

## 10. peso_vaquillonas
```{r}
name <- "peso_vaquillonas"
peso_vaquillonas <- import(paste0(path_i, "/", name, ".xlsx"))
str(peso_vaquillonas)
```
```{r}
peso_vaquillonas <- peso_vaquillonas %>%
  mutate(
    AN = as.factor(AN)
  )
str(peso_vaquillonas)
```
```{r}
use_data(peso_vaquillonas)
```

## 11. estrogeno
```{r}
name <- "estrogeno"
estrogeno <- import(paste0(path_i, "/", name, ".xlsx"))
str(estrogeno)
```
```{r}
estrogeno <- estrogeno %>%
  mutate(
    SO = as.factor(SO)
  )
str(estrogeno)
```
```{r}
use_data(estrogeno)
```

## 12. lechuga
```{r}
name <- "lechuga"
lechuga <- import(paste0(path_i, "/", name, ".xlsx"))
str(lechuga)
```
```{r}
lechuga <- lechuga %>%
  mutate(
    Dosis_ord = as.ordered(Dosis),
    Dosis_chr = as.factor(Dosis_chr)
  ) %>%
  select(Dosis, Dosis_ord, everything())
str(lechuga)
```
```{r}
use_data(lechuga)
```

## 13. gallinas
```{r}
name <- "gallinas"
gallinas <- import(paste0(path_i, "/", name, ".xlsx"))
str(gallinas)
```
```{r}
gallinas <- gallinas %>%
  mutate(
    TR = as.factor(TR)
  )
str(gallinas)
```
```{r}
use_data(gallinas)
```

## 14. pH_laboratorio
```{r}
name <- "pH_laboratorio"
pH_laboratorio <- import(paste0(path_i, "/", name, ".xlsx"))
str(pH_laboratorio)
```
```{r}
pH_laboratorio <- pH_laboratorio %>%
  mutate(
    Dispositivo = as.factor(Dispositivo),
    Muestra = as.factor(Muestra)
  )
str(pH_laboratorio)
```
```{r}
use_data(pH_laboratorio)
```

## 15. conservante_frutilla
```{r}
name <- "conservante_frutilla"
conservante_frutilla <- import(paste0(path_i, "/", name, ".xlsx"))
str(conservante_frutilla)
```
```{r}
conservante_frutilla <- conservante_frutilla %>%
  mutate(
    Tratamiento = as.factor(Tratamiento)
  )
str(conservante_frutilla)
```
```{r}
use_data(conservante_frutilla)
```

## 16. hibridos_maiz
```{r}
name <- "hibridos_maiz"
hibridos_maiz <- import(paste0(path_i, "/", name, ".xlsx"))
str(hibridos_maiz)
```
```{r}
hibridos_maiz <- hibridos_maiz %>%
  mutate(
    Hibrido = as.factor(Hibrido)
  )
str(hibridos_maiz)
```
```{r}
use_data(hibridos_maiz)
```

## 17. dieta_pavos
```{r}
name <- "dieta_pavos"
dieta_pavos <- import(paste0(path_i, "/", name, ".xlsx"))
str(dieta_pavos)
```
```{r}
dieta_pavos <- dieta_pavos %>%
  mutate(
    Dieta = as.factor(Dieta)
  )
str(dieta_pavos)
```
```{r}
use_data(dieta_pavos)
```

## 18. nematodes_durazno
```{r}
name <- "nematodes_durazno"
nematodes_durazno <- import(paste0(path_i, "/", name, ".xlsx"))
str(nematodes_durazno)
```
```{r}
nematodes_durazno <- nematodes_durazno %>%
  mutate(
    Tratamiento = as.factor(Tratamiento)
  )
str(nematodes_durazno)
```
```{r}
use_data(nematodes_durazno)
```

## 19. dietas_novillos
```{r}
name <- "dietas_novillos"
dietas_novillos <- import(paste0(path_i, "/", name, ".xlsx"))
str(dietas_novillos)
```
```{r}
dietas_novillos <- dietas_novillos %>%
  mutate(
    Dieta = as.factor(Dieta),
    Animal = as.factor(Animal)
  )
str(dietas_novillos)
```
```{r}
use_data(dietas_novillos)
```

## 20. fertilizante_pastizal
```{r}
name <- "fertilizante_pastizal"
fertilizante_pastizal <- import(paste0(path_i, "/", name, ".xlsx"))
str(fertilizante_pastizal)
```
```{r}
fertilizante_pastizal <- fertilizante_pastizal %>%
  mutate(
    Bloque = as.factor(Bloque),
    Tratamiento = as.factor(Tratamiento)
  )
str(fertilizante_pastizal)
```
```{r}
use_data(fertilizante_pastizal)
```

## 21. fibra_quimico
```{r}
name <- "fibra_quimico"
fibra_quimico <- import(paste0(path_i, "/", name, ".xlsx"))
str(fibra_quimico)
```
```{r}
fibra_quimico <- fibra_quimico %>%
  mutate(
    BL = as.factor(BL),
    CQ = as.factor(CQ)
  )
str(fibra_quimico)
```
```{r}
use_data(fibra_quimico)
```

## 22. gladiolos
```{r}
name <- "gladiolos"
gladiolos <- import(paste0(path_i, "/", name, ".xlsx"))
str(gladiolos)
```
```{r}
gladiolos <- gladiolos %>%
  mutate(
    BL = as.factor(BL),
    TR = as.factor(TR)
  )
str(gladiolos)
```
```{r}
use_data(gladiolos)
```

## 23. invernadero_spartina
```{r}
name <- "invernadero_spartina"
invernadero_spartina <- import(paste0(path_i, "/", name, ".xlsx"))
str(invernadero_spartina)
```
```{r}
invernadero_spartina <- invernadero_spartina %>%
  mutate(
    TR = as.factor(TR),
    BL = as.factor(BL)
  )
str(invernadero_spartina)
```
```{r}
use_data(invernadero_spartina)
```

## 24. irrigacion_naranjo
```{r}
name <- "irrigacion_naranjo"
irrigacion_naranjo <- import(paste0(path_i, "/", name, ".xlsx"))
str(irrigacion_naranjo)
```
```{r}
irrigacion_naranjo <- irrigacion_naranjo %>%
  mutate(
    BL = as.factor(BL),
    TR = as.factor(TR)
  )
str(irrigacion_naranjo)
```
```{r}
use_data(irrigacion_naranjo)
```

## 25. nabos
```{r}
name <- "nabos"
nabos <- import(paste0(path_i, "/", name, ".xlsx"))
str(nabos)
```
```{r}
nabos <- nabos %>%
  mutate(
    BL = as.factor(BL),
    TR = as.factor(TR)
  )
str(nabos)
```
```{r}
use_data(nabos)
```

## 26. resist_algodon
```{r}
name <- "resist_algodon"
resist_algodon <- import(paste0(path_i, "/", name, ".xlsx"))
str(resist_algodon)
```
```{r}
resist_algodon <- resist_algodon %>%
  mutate(
    BL = as.factor(BL),
    AL_ord = as.ordered(AL)
  ) %>%
  select(BL, AL, AL_ord, everything())
str(resist_algodon)
```
```{r}
use_data(resist_algodon)
```

## 27. rollos_tela
```{r}
name <- "rollos_tela"
rollos_tela <- import(paste0(path_i, "/", name, ".xlsx"))
str(rollos_tela)
```
```{r}
rollos_tela <- rollos_tela %>%
  mutate(
    BL = as.factor(BL),
    AQ = as.factor(AQ)
  )
str(rollos_tela)
```
```{r}
use_data(rollos_tela)
```

## 28. sorgo_urea
```{r}
name <- "sorgo_urea"
sorgo_urea <- import(paste0(path_i, "/", name, ".xlsx"))
str(sorgo_urea)
```
```{r}
sorgo_urea <- sorgo_urea %>%
  mutate(
    BL = as.factor(BL),
    DO_ord = as.ordered(DO)
  ) %>%
  select(BL, DO, DO_ord, everything())
str(sorgo_urea)
```
```{r}
use_data(sorgo_urea)
```

## 29. insecticida_poroto
```{r}
name <- "insecticida_poroto"
insecticida_poroto <- import(paste0(path_i, "/", name, ".xlsx"))
str(insecticida_poroto)
```
```{r}
insecticida_poroto <- insecticida_poroto %>%
  mutate(
    Bloque = as.factor(Bloque),
    Insecticida = as.factor(Insecticida)
  )
str(insecticida_poroto)
```
```{r}
use_data(insecticida_poroto)
```

## 30. larvas_cesped
```{r}
name <- "larvas_cesped"
larvas_cesped <- import(paste0(path_i, "/", name, ".xlsx"))
str(larvas_cesped)
```
```{r}
larvas_cesped <- larvas_cesped %>%
  mutate(
    Sitio = as.factor(Sitio),
    Tratamiento = as.factor(Tratamiento),
    Parcela = as.factor(Parcela),
    Muestra = as.factor(Muestra)
  )
str(larvas_cesped)
```
```{r}
use_data(larvas_cesped)
```

## 31. cana_azucar
```{r}
name <- "cana_azucar"
cana_azucar <- import(paste0(path_i, "/", name, ".xlsx"))
str(cana_azucar)
```
```{r}
cana_azucar <- cana_azucar %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    VAR = as.factor(VAR),
    RTO = as.numeric(RTO)
  )
str(cana_azucar)
```
```{r}
use_data(cana_azucar)
```

## 32. hormona_ovario
```{r}
name <- "hormona_ovario"
hormona_ovario <- import(paste0(path_i, "/", name, ".xlsx"))
str(hormona_ovario)
```
```{r}
hormona_ovario <- hormona_ovario %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    HORMONA = as.factor(HORMONA),
    PESO = as.numeric(PESO)
  )
str(hormona_ovario)
```
```{r}
use_data(hormona_ovario)
```

## 33. inyeccion_vaquillas
```{r}
name <- "inyeccion_vaquillas"
inyeccion_vaquillas <- import(paste0(path_i, "/", name, ".xlsx"))
str(inyeccion_vaquillas)
```
```{r}
inyeccion_vaquillas <- inyeccion_vaquillas %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    D = as.factor(D),
    RTA = as.numeric(RTA),
    D_num = as.numeric(D_num),
    D_ord = as.ordered(D_num)
  )
str(inyeccion_vaquillas)
```
```{r}
use_data(inyeccion_vaquillas)
```

## 34. prolactina_vacas
```{r}
name <- "prolactina_vacas"
prolactina_vacas <- import(paste0(path_i, "/", name, ".xlsx"))
str(prolactina_vacas)
```
```{r}
prolactina_vacas <- prolactina_vacas %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    DOSIS = as.factor(DOSIS),
    PICO = as.numeric(PICO),
    DOSIS_num = as.numeric(DOSIS_num),
    DOSIS_ord = as.ordered(DOSIS_num)
  )
str(prolactina_vacas)
```
```{r}
use_data(prolactina_vacas)
```

## 35. tiempo_reaccion
```{r}
name <- "tiempo_reaccion"
tiempo_reaccion <- import(paste0(path_i, "/", name, ".xlsx"))
str(tiempo_reaccion)
```
```{r}
tiempo_reaccion <- tiempo_reaccion %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    INGREDIENTE = as.factor(INGREDIENTE),
    TIEMPO = as.numeric(TIEMPO)
  )
str(tiempo_reaccion)
```
```{r}
use_data(tiempo_reaccion)
```

## 36. variedad_trigo
```{r}
name <- "variedad_trigo"
variedad_trigo <- import(paste0(path_i, "/", name, ".xlsx"))
str(variedad_trigo)
```
```{r}
variedad_trigo <- variedad_trigo %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    VAR = as.factor(VAR),
    REND = as.numeric(REND)
  )
str(variedad_trigo)
```
```{r}
use_data(variedad_trigo)
```

## 37. labores_remolacha
```{r}
name <- "labores_remolacha"
labores_remolacha <- import(paste0(path_i, "/", name, ".xlsx"))
str(labores_remolacha)
```
```{r}
labores_remolacha <- labores_remolacha %>%
  mutate(
    F = as.factor(F),
    C = as.factor(C),
    LAB = as.factor(LAB),
    RTO = as.numeric(RTO)
  )
str(labores_remolacha)
```
```{r}
use_data(labores_remolacha)
```

## 38. raciones_pollos
```{r}
name <- "raciones_pollos"
raciones_pollos <- import(paste0(path_i, "/", name, ".xlsx"))
str(raciones_pollos)
```
```{r}
raciones_pollos <- raciones_pollos %>%
  mutate(
    Pisos = as.factor(Pisos),
    Casilleros = as.factor(Casilleros),
    Racion = as.factor(Racion),
    Peso = as.numeric(Peso)
  )
str(raciones_pollos)
```
```{r}
use_data(raciones_pollos)
```

## 39. semillas_trigo
```{r}
name <- "semillas_trigo"
semillas_trigo <- import(paste0(path_i, "/", name, ".xlsx"))
str(semillas_trigo)
```
```{r}
semillas_trigo <- semillas_trigo %>%
  mutate(
    Abonos = as.factor(Abonos),
    Insecticidas = as.factor(Insecticidas),
    Semilla = as.factor(Semilla),
    Rendimiento = as.numeric(Rendimiento)
  )
str(semillas_trigo)
```
```{r}
use_data(semillas_trigo)
```

## 40. conc_glucosa
```{r}
name <- "Conc_glucosa"
conc_glucosa <- import(paste0(path_i, "/", name, ".xlsx"))
str(conc_glucosa)
```
```{r}
conc_glucosa <- conc_glucosa %>%
  mutate(
    Metodo = as.factor(Metodo),
    Nivel = as.factor(Nivel),
    Concentracion = as.numeric(Concentracion),
    repeticion = as.factor(repeticion)
  )
str(conc_glucosa)
```
```{r}
use_data(conc_glucosa)
```

## 41. energia_abejas
```{r}
name <- "Energia_abejas"
energia_abejas <- import(paste0(path_i, "/", name, ".xlsx"))
str(energia_abejas)
```
```{r}
energia_abejas <- energia_abejas %>%
  mutate(
    Temp = as.numeric(Temp),
    Visc = as.numeric(Visc),
    Energia = as.numeric(Energia),
    Temp_ord = as.ordered(Temp),
    Visc_ord = as.ordered(Visc),
    repeticion = as.factor(repeticion)
  )
str(energia_abejas)
```
```{r}
use_data(energia_abejas)
```

## 42. fijacion_N
```{r}
name <- "Fijacion_N"
fijacion_N <- import(paste0(path_i, "/", name, ".xlsx"))
str(fijacion_N)
```
```{r}
fijacion_N <- fijacion_N %>%
  mutate(
    Cultivo = as.factor(Cultivo),
    N = as.numeric(N),
    acetileno = as.numeric(acetileno),
    N_ord = as.ordered(N),
    repeticion = as.factor(repeticion)
  )
str(fijacion_N)
```
```{r}
use_data(fijacion_N)
```

## 43. met_pesados
```{r}
name <- "Met_pesados"
met_pesados <- import(paste0(path_i, "/", name, ".xlsx"))
str(met_pesados)
```
```{r}
met_pesados <- met_pesados %>%
  mutate(
    Ciudad = as.factor(Ciudad),
    Dosis = as.numeric(Dosis),
    zinc = as.numeric(zinc),
    Dosis_ord = as.ordered(Dosis),
    repeticion = as.factor(repeticion)
  )
str(met_pesados)
```
```{r}
use_data(met_pesados)
```

## 44. sal_cebada
```{r}
name <- "Sal_cebada"
sal_cebada <- import(paste0(path_i, "/", name, ".xlsx"))
str(sal_cebada)
```
```{r}
sal_cebada <- sal_cebada %>%
  mutate(
    Salinidad = as.numeric(Salinidad),
    Edad = as.numeric(Edad),
    Consumo = as.numeric(Consumo),
    Salinidad_ord = as.ordered(Salinidad),
    Edad_ord = as.ordered(Edad),
    repeticion = as.factor(repeticion)
  )
str(sal_cebada)
```
```{r}
use_data(sal_cebada)
```

## 45. sal_suelo
```{r}
name <- "Sal_suelo"
sal_suelo <- import(paste0(path_i, "/", name, ".xlsx"))
str(sal_suelo)
```
```{r}
sal_suelo <- sal_suelo %>%
  mutate(
    Salinidad = as.numeric(Salinidad),
    Salinidad_ord = as.ordered(Salinidad),
    Agua = as.numeric(Agua),
    Agua_ord = as.ordered(Agua),
    Textura = as.factor(Textura),
    EC = as.numeric(EC),
    repeticion = as.factor(repeticion)
  )
str(sal_suelo)
```
```{r}
use_data(sal_suelo)
```

## 46. fert_melon
```{r}
name <- "fert_melon"
fert_melon <- import(paste0(path_i, "/", name, ".xlsx"))
str(fert_melon)
```
```{r}
fert_melon <- fert_melon %>%
  mutate(
    Fila = as.factor(Fila),
    Column = as.factor(Column),
    Tratamiento = as.factor(Tratamiento),
    rend = as.numeric(rend)
  )
str(fert_melon)
```
```{r}
use_data(fert_melon)
```

## 47. inhibidor_N
```{r}
name <- "inhibidor_N"
inhibidor_N <- import(paste0(path_i, "/", name, ".xlsx"))
str(inhibidor_N)
```
```{r}
inhibidor_N <- inhibidor_N %>%
  mutate(
    bloque = as.factor(bloque),
    inhibidor = as.factor(inhibidor),
    Nsuelo = as.factor(Nsuelo),
    Nabsorbido = as.numeric(Nabsorbido)
  )
str(inhibidor_N)
```
```{r}
use_data(inhibidor_N)
```

## 48. soja_pd
En parcelas divididas no se agrego la columna parcela aun, queda pendiente
```{r}
name <- "soja_pd"
soja_pd <- import(paste0(path_i, "/", name, ".xlsx"))
str(soja_pd)
```
```{r}
soja_pd <- soja_pd %>%
  mutate(
    variedad = as.factor(variedad),
    espaciamiento = as.numeric(espaciamiento),
    bloque = as.factor(bloque),
    rendimiento = as.numeric(rendimiento),
    espaciamiento_ord = as.ordered(espaciamiento)
  )
str(soja_pd)
```
```{r}
use_data(soja_pd)
```

## 49. semillas_pd
```{r}
name <- "semillas_pd"
semillas_pd <- import(paste0(path_i, "/", name, ".xlsx"))
str(semillas_pd)
```
```{r}
semillas_pd <- semillas_pd %>%
  mutate(
    lote = as.factor(lote),
    bloque = as.factor(bloque),
    tratamiento = as.factor(tratamiento),
    rendimiento = as.numeric(rendimiento)
  )
str(semillas_pd)
```
```{r}
use_data(semillas_pd)
```

## 50. arroz_pd
```{r}
name <- "arroz_pd"
arroz_pd <- import(paste0(path_i, "/", name, ".xlsx"))
str(arroz_pd)
```
```{r}
arroz_pd <- arroz_pd %>%
  mutate(
    Lamina = as.factor(Lamina),
    Variedad = as.factor(Variedad),
    Repetición = as.factor(Repetición),
    Rend = as.numeric(Rend)
  )
str(arroz_pd)
```
```{r}
use_data(arroz_pd)
```

## 51. cana_pd
```{r}
name <- "caña_pd"
cana_pd <- import(paste0(path_i, "/", name, ".xlsx"))
str(cana_pd)
```
```{r}
cana_pd <- cana_pd %>%
  mutate(
    Fecha = as.factor(Fecha),
    Método = as.factor(Método),
    Bloque = as.factor(Bloque),
    Rend = as.numeric(Rend)
  )
str(cana_pd)
```
```{r}
use_data(cana_pd)
```

## 52. maiz2_pd
```{r}
name <- "maiz2_pd"
maiz2_pd <- import(paste0(path_i, "/", name, ".xlsx"))
str(maiz2_pd)
```
```{r}
maiz2_pd <- maiz2_pd %>%
  mutate(
    Bloque = as.factor(Bloque),
    Aplicacion = as.factor(Aplicacion),
    Abono = as.factor(Abono),
    Rend = as.numeric(Rend)
  )
str(maiz2_pd)
```
```{r}
use_data(maiz2_pd)
```

## 53. trigo_zona_ciclo
```{r}
name <- "trigo_zona_ciclo"
trigo_zona_ciclo <- import(paste0(path_i, "/", name, ".xlsx"))
str(trigo_zona_ciclo)
```
```{r}
trigo_zona_ciclo <- trigo_zona_ciclo %>%
  mutate(
    Zona = as.factor(Zona),
    Ciclo = as.factor(Ciclo),
    Rep = as.factor(Rep),
    Rinde = as.numeric(Rinde)
  )
str(trigo_zona_ciclo)
```
```{r}
use_data(trigo_zona_ciclo)
```

## 54. trigo_fungicidas_momentos
```{r}
name <- "trigo_fungicidas_momentos"
trigo_fungicidas_momentos <- import(paste0(path_i, "/", name, ".xlsx"))
str(trigo_fungicidas_momentos)
```
```{r}
trigo_fungicidas_momentos <- trigo_fungicidas_momentos %>%
  mutate(
    Fungicida = as.factor(Fungicida),
    Momento = as.factor(Momento),
    Bloque = as.factor(Bloque),
    y = as.numeric(y)
  )
str(trigo_fungicidas_momentos)
```
```{r}
use_data(trigo_fungicidas_momentos)
```

## 55. digest_in_vitro
```{r}
name <- "digest_in_vitro"
digest_in_vitro <- import(paste0(path_i, "/", name, ".xlsx"))
str(digest_in_vitro)
```
```{r}
digest_in_vitro <- digest_in_vitro %>%
  mutate(
    Dosis = as.numeric(Dosis),
    Tubo = as.factor(Tubo),
    dig48 = as.numeric(dig48),
    Dosis_ord = as.ordered(Dosis)
  )
str(digest_in_vitro)
```
```{r}
use_data(digest_in_vitro)
```
